### 2019-05-22 doc/chapters/using_bitcoins.tex
changed subsections
chapter intro

\chapter{Using Bitcoin-S}
\label{chap:using_bitcoins}

@@

\section{{Bugfix for noDublicate}}

>>>>

\chapter{Using Bitcoin-S-Core}
\label{chap:using_bitcoins}
This chapter describes the relevant parts needed to verify that a non-coinbase transaction cannot generate new coins in Bitcoin-S-Core.
We will see, how to create valid and invalid transactions with Bitcoin-S-Core and how this transactions are validated against the described property.

@@
